Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-05 writeup/gz_hubble_data.tex
Typo in boosted figure reference

Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{:debiased_corrections}). As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}. There are only eight galaxies that were strongly boosted ($p_\mathrm{features,raw}<0.2$ and $p_\mathrm{features,best} > 0.5$) in GZH and also appears in the CANDELS expert sample. Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky. The \pbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates. One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging. Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.

>>>>

Few galaxies in the sample have sufficiently high corrections to completely change them from being confidently smooth to featured following the bias correction (Figure~\ref{fig:debiased_corrections}). As a check, highly boosted galaxies are compared to the expert classifications in the CANDELS catalog \citep{kar15}. There are only eight galaxies that were strongly boosted ($p_\mathrm{features,raw}<0.2$ and $p_\mathrm{features,best} > 0.5$) in GZH and also appears in the CANDELS expert sample. Of those eight galaxies, \citet{kar15} classifies 5 as spheroids, 2 as disks, and 1 as irregular/disky. The \pbest{} values for GZH are all between 0.5 and 0.6, making them intermediate disk candidates. One of the spheroids has hints of an interaction or minor merger to the south that may have been missed by the CANDELS experts, but almost all images are dim and with very low surface brightnesses in the ACS imaging, making positive identification challenging. Since the surveys use different rest-frame filters and the overlap sample is tiny, though, detailed comparisons between the overall morphologies are highly difficult.
